Supplementary Materials

### 2023-10-27 analysis/supplementary-materials/supp-mat.qmd
round 1 of modifications based on reviewer comments

The samples in the replication batch were processed in the same way, but
analysed on equipment used exclusively for oral samples.

@@

```{r}
#| label: tbl-uhplc-batch-1
#| tbl-cap: "Results from the UHPLC analysis first batch. Quantity of compound in the dissolved calculus, represented in ng."
uhplc_calculus_long %>%
  filter(batch == "batch1") %>%
  select(!c(sample, conc, extraction, batch, presence)) %>%
  pivot_wider(names_from = "compound", values_from = "quant") %>% 
  knitr::kable()
```

```{r}
#| label: tbl-uhplc-batch-2
#| tbl-cap: "Results from the UHPLC analysis second batch. Quantity of compound in calculus after third wash, represented in ng."
uhplc_calculus_long %>%
  filter(batch == "batch2") %>%
  pivot_wider(names_from = "compound", values_from = "quant") %>%
  select(!c(extraction, batch)) %>% 
  knitr::kable()
```

>>>>

The samples in the replication batch were processed in the same way, but
analysed on different equipment used exclusively for oral samples.

Raw quantities of compounds detected in the dissolved calculus from batches
1 and 2 are presented in @tbl-uhplc-batch-1 and @tbl-uhplc-batch-2. Since
these tables may or may not be legible in PDF format, not to mention that they
don't adhere to FAIR principles in this format, the raw data can be downloaded
from Zenodo (https://doi.org/10.5281/zenodo.8061483).

@@

```{r}
#| label: tbl-uhplc-batch-1
#| tbl-cap: "Results from the UHPLC analysis first batch. Quantity of compound in the dissolved calculus, represented in ng and rounded to 3 digits after the decimal."
uhplc_calculus_long %>%
  filter(batch == "batch1") %>%
  mutate(quant = round(quant, 3)) %>% 
  select(!c(sample, conc, extraction, batch, presence)) %>%
  pivot_wider(names_from = "compound", values_from = "quant") %>% 
  knitr::kable()
```

```{r}
#| label: tbl-uhplc-batch-2
#| tbl-cap: "Results from the UHPLC analysis second batch. Quantity of compound in calculus after third wash, represented in ng and rounded to 3 digits after the decimal."
uhplc_calculus_long %>%
  filter(batch == "batch2") %>%
  mutate(quant = round(quant, 3)) %>% 
  pivot_wider(names_from = "compound", values_from = "quant") %>%
  select(!c(extraction, batch)) %>% 
  knitr::kable()
```
